---
title: 'Task 3: Bootstrapping'
author: "Allison Hacker"
date: "3/2/2021"
output: 
  html_document:
    theme: paper
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(janitor)
library(boot)
```

### Bootstrapped proportions
```{r}
# create vector of student survey data (n= 36, yes(1) = 22, no(0) = 14)
data = c(rep(1, 22), rep(0, 14))

# view(data)

# make function calculate proportion who did experience hostility/exclusion
# since yes = 1 and no = 0, mean = proportion who responded yes

prop_fun <- function(x, i){
  mean(x[i])
}

# create 10,000 bootstrap samples
boot_10k <- boot(data, statistic = prop_fun, R = 10000)

# look at the outputs
# boot_10k
# boot_10k$t0 

# make vector of bootstrap sample means into a data frame for graphing
boot_10k_df <- data.frame(bs_mean = boot_10k$t)

# make histogram of 10,000 bootstrap means aka proportions:
ggplot(data = boot_10k_df, aes(x = bs_mean)) +
  geom_histogram()+
  theme_minimal()+
  labs(x = "Proportion of nonbinary students who experienced\nexclusionary, hostile or intimidating behavior", y = "Count")

```


### Confidence interval
```{r, collapse=TRUE}
# calculate 95% confidence interval for bootstrapped sample means
boot.ci(boot_10k, conf = 0.95)
```


The proportion of nonbinary/genderqueer students who reported experiencing exclusionary, hostile, or intimidating behavior at UCSB was 61% with a 95% confidence interval of 45.3% to 77.2%. This means that 95 out of 100 times, we expect the actual proportion of all nonbinary/genderqueer students at UCSB who experienced exclusionary, hostile, or intimidating behavior to fall within this range.

**Data source:** 2014 UCSB Campus Climate Project Final Report (prepared by Rankin & Associates Consulting)
